# spocc {#spocc}

## What is spocc? {#what-spocc}

[spocc][] is an R package that is a single user interface to occurrence data.

`spocc` currently interfaces with ten major biodiversity repositories

1. [Global Biodiversity Information Facility (GBIF)][gbif] (via `rgbif`)
2. [Berkeley Ecoengine][ecoengine] (via `ecoengine`)
3. [iNaturalist][inat]
4. [VertNet][vertnet] (via `rvertnet`)
5. [Biodiversity Information Serving Our Nation][bison] (via `rbison`)
6. [eBird][ebird] (via `rebird`)
7. [AntWeb][antweb] (via `AntWeb`)
8. [iDigBio][idigbio] (via `ridigbio`)
9. [OBIS][obis]
10. [Atlas of Living Australia][ala]

## Basic example {#basic-example}

Load `spocc` and request data for a given taxonomic name, for each of three different data sources, specify options across all data sources (e.g., `limit` number of records), and options for specific data sources (using `gbifopts = list()`, etc. for each data source).

```{r}
library(spocc)
out <- occ(query = 'Setophaga caerulescens', from = c('gbif','bison','inat'), limit = 3, gbifopts = list(country = 'US'))
```

Access GBIF data

```{r collapse=TRUE}
out$gbif
```

Access BISON data

```{r collapse=TRUE}
out$bison
```

Access iNaturalist data

```{r collapse=TRUE}
out$inat
```

[spocc]: https://github.com/ropensci/spocc
[gbif]: https://github.com/ropensci/rgbif
[vertnet]: https://github.com/ropensci/rvertnet
[bison]: https://github.com/ropensci/rbison
[inat]: https://github.com/ropensci/rinat
[taxize]: https://github.com/ropensci/taxize
[ecoengine]: https://github.com/ropensci/ecoengine
[antweb]: http://antweb.org/
[idigbio]: https://www.idigbio.org/
[obis]: http://www.iobis.org/
[ebird]: http://ebird.org/content/ebird/
[ala]: http://www.ala.org.au/
