```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

# rvertnet {#rvertnet}

## What is rvertnet? {#what-rvertnet}

[rvertnet][] is an R package for interacting with [VertNet.org](http://vertnet.org/).

VertNet.org API docs: <https://github.com/VertNet/webapp/wiki/The-API-search-function>




## Basic example {#rvertnet-basic-example}

Load `rvertnet`

```{r}
library(rvertnet)
```

Search for _Aves_ in the state of _California_, limit to 10 records

```{r messages=FALSE}
res <- searchbyterm(class = "Aves", state = "California", lim = 10)
```

metadata

```{r collapse = TRUE}
res$meta
```

data. A `tibble` is given back:

```{r collapse = TRUE}
res$data
```

Search for _Mustela nigripes_ in the states of _Wyoming_ or _South Dakota_, 
limit to 20 records

```{r collapse = TRUE}
res <- searchbyterm(specificepithet = "nigripes", 
    state = "(wyoming OR south dakota)", limit = 20)
res$data
```

### downstream data manipulation

You can pass the data object directly on to `dplyr` functions. Here, we get a 
table of record counts by species in descending order.

```{r collapse = TRUE, cache = TRUE}
library("dplyr")
out <- searchbyterm(genus = "Ochotona", limit = 800)
out$data %>%
  group_by(scientificname) %>%
  summarise(count = length(scientificname)) %>%
  arrange(desc(count))
```


[rvertnet]: https://github.com/ropensci/rvertnet
